---
title: Presentation inside the REPL
author: Sebastian Warnholz
email: wahani@gmail.com
---

```{r eval = TRUE, echo = FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

# slider -- Presentations inside the REPL

author: Sebastian Warnholz  
date: `r Sys.Date()`  
email: wahani@gmail.com  


# Outline

- Make presentations inside the R REPL
- You don't need the switch between presentation modes
    - during programming tutorials
    - while introducing packages in the console
- The Rmd is preprocessed with knitr:
    - take advantage of rmarkdown
    - take advantage of markdown and pandoc



# Start a presentation

- We start a presentation by
    - converting the rmarkdown document
    - and *loading* the presentation

//code
```{r}
if (FALSE) {
  presi <- slider::loadPresentation("my-presentation.Rmd")
  presi$start()
}
```


# Presentation mode

- After starting a presentation we are in the *presentation mode*
- This means you have some basic control options:
    - `n` -- next slide
    - `p` -- previous slide
    - `!` -- evaluate code on slide
    - `!!` -- quitely evaluate code on slide
    - `f` -- first slide
    - `l` -- last slide
    - `?` -- see this list
    - `q` -- quit



# Evaluation of code

//code
```{r}
x <- 1
```

- Enumeration
    - With some indent
- More code:

//code
```{r}
y <- 2
```

# Some more code

And text...

//code
```{r}
z <- 3
```
