---
title: Presentation inside the REPL
author: Sebastian Warnholz
email: wahani@gmail.com
---

```{r eval = TRUE, echo = FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

# slider -- Presentations inside the REPL

author: Sebastian Warnholz  
date: `r Sys.Date()`  
email: wahani@gmail.com  


# Outline

- Make presentations inside the R REPL
- You don't need the switch between presentation modes
    - during programming tutorials
    - while introducing packages in the console
- The Rmd is preprocessed with knitr:
    - take advantage of rmarkdown
    - take advantage of markdown and pandoc
    - continue to work in the REPL
- Since we are in the REPL we do not get a whole lot of formating options

# Start a presentation

- We start a presentation by
    - converting the rmarkdown document
    - and *loading* the presentation

```{r}
if (FALSE) {
  presi <- slider::loadPresentation("my-presentation.Rmd")
  presi$start()
}
```


# Presentation mode

- After starting a presentation we are in the *presentation mode*
- This means you have some basic control options:
    - `n` -- next slide
    - `p` -- previous slide
    - `!` -- evaluate code on slide
    - `!!` -- quitely evaluate code on slide
    - `f` -- first slide
    - `l` -- last slide
    - `?` -- see this list
    - `q` -- quit
